```{r, echo=FALSE, results="hide"}
Sys.setlocale("LC_ALL","C")
```
## 1. Code for reading in the dataset and/or processing the data
______________________________________________________________
```{r}
library(data.table)
activity_dt<-data.table(read.csv("activity.csv"))
activity_dt$date<-as.POSIXct(activity_dt$date, "%Y-%m-%d")
activity_dt$interval<-as.factor(activity_dt$interval)

```

## 2.Histogram of the total number of steps taken each day
________________________________________________________

Calculation the total number of steps taken per day
```{r}
steps_taken_per_day<-tapply(activity_dt$steps,activity_dt$date,sum, na.rm=TRUE)
```

Histogram of the total number of steps taken each day
```{r}
hist(steps_taken_per_day, main="Total number of steps taken per day", 
     xlab="steps",breaks=10)
```

## 3. Mean and median number of steps taken each day
____________________________________________________
```{r}
mean(steps_taken_per_day)
median(steps_taken_per_day)
```



##4. Time series plot of the average number of steps taken
___________________________________________________________
Time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
avg_steps_per_interval<-tapply(activity_dt$steps,activity_dt$interval,mean, na.rm=TRUE)
plot(names(avg_steps_per_interval),avg_steps_per_interval,xlab="5-minute interval", ylab="average number of steps", main="average daily activity",type = "l")
```


## 5. The 5-minute interval that, on average, contains the maximum number of steps
__________________________________________________________________________________
```{r}
names(avg_steps_per_interval)[which.max(avg_steps_per_interval)]
```

## 6. Code to describe and show a strategy for imputing missing data

The total number of missing values in the dataset 
```{r}
nrow(activity_dt[is.na(activity_dt$steps),])
```

I use the mean for that 5-minute interval to Imputing missing values.
```{r}
activity_dt[,interval_mean:=mean(steps,na.rm=TRUE), by=interval]
NA_row<-is.na(activity_dt$steps)
activity_dt$new_steps<-activity_dt$steps
activity_dt$new_steps[NA_row]<-activity_dt$interval_mean[NA_row]
```


Create a new dataset that is equal to the original dataset but with the missing data filled in
```{r}
activity_dt_new<-activity_dt[,c("date","interval","new_steps"), with=FALSE]
```


## 7. Histogram of the total number of steps taken each day after missing values are imputed
____________________________________________________________________________________________
Two histograms of the total number of steps taken each day and Calculate.  
Befor and after.
```{r}
steps_taken_per_day_new<-tapply(activity_dt_new$new_steps,activity_dt_new$date,
                                sum, na.rm=TRUE)
par(mfrow=c(2,1),mar=c(4,4,2,1))
hist(steps_taken_per_day, main="Total number of steps taken per day without NA", 
     xlab="steps",breaks=10)
hist(steps_taken_per_day_new, main="NEW Total number of steps taken per day  
     after missing values were imputed", xlab="new steps",breaks=10)

```

Mean and median total number of steps taken per day
```{r}
mean(steps_taken_per_day_new)
median(steps_taken_per_day_new)
```
Values differ from the estimates from the first part of the assignment


##8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
_______________________________________________________________________________________
```{r}
activity_dt_new[,day_name:=weekdays(date,TRUE)]
day_name=c("Mon","Tue","Wed","Thu","Fri","Sat","Sun")
week_part=c(rep("weekday",5),rep("weekend",2))
week_table<-data.table(day_name,week_part)
setkey(activity_dt_new,day_name)
setkey(week_table,day_name)
activity_dt_new<-merge(x = activity_dt_new, y = week_table, by = "day_name", 
                       all.x = TRUE)
activity_dt_new$week_part<-as.factor(activity_dt_new$week_part)
```

The panel plot containing a time series plot  of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis)
```{r}
weekday<-activity_dt_new[activity_dt_new$week_part=="weekday"]
weekend<-activity_dt_new[activity_dt_new$week_part=="weekend"]

avg_steps_per_interval_weekday=tapply(weekday$new_steps,weekday$interval,
                                      mean, na.rm=TRUE)
avg_steps_per_interval_weekend=tapply(weekend$new_steps,weekend$interval,
                                      mean, na.rm=TRUE)

par(mfrow=c(2,1),mar=c(4,4,2,1))
plot(names(avg_steps_per_interval_weekday),avg_steps_per_interval_weekday,
     xlab="5-minute interval", ylab="average number of steps", 
     main="Weekday average daily activity",type = "l")
plot(names(avg_steps_per_interval_weekday),avg_steps_per_interval_weekend,
     xlab="5-minute interval", ylab="average number of steps", 
     main="Weekend average daily activity",type = "l")
```
